Spikes demo

### 2018-11-06 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

Launch R, and change the working directory to be the `analysis` folder
inside your local copy of the `smash-paper` git repository.

Install some of the packages used here, and in the code below:

@@

See the "Session Info" at the bottom of this example for the versions
of the software and R packages that were used to generate the results
shown below.

>>>>

Launch R, and change the working directory to be the "analysis" folder
inside your local copy of the git repository.

Install some of the packages used here and in the code below:

@@

See the "Session Info" at the bottom for the versions of the software
and R packages that were used to generate the results shown below.
